Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
Ajout d'infos sur la database

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.
\section{Related works}

@@

    \begin{table}[!t]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

>>>>

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.

    \textbf{WE WILL WORK WITH ONLY ONE PROVIDER [ptet le mettre ailleurs].}
\section{Related works}

@@

    This database is updated every quarter. For instance, the own we used was published on 28th March 2024 \cite{main_database_hist}.

    On the site there is a chat where we can ask questions about the databases \cite{main_database_chat}.

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

    \begin{figure}[!t]
        \centering
        \boxed{\includegraphics[width=2.5in]{images/data_analysis/with_techno.png}}
        \caption{Breakdown, by operator, of the number of sites containing a given technology}
        \label{fig:data_technos}
    \end{figure}

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}
